\documentclass{ximera}
\title{Privacy policy}

\begin{document}
\begin{abstract}
  This privacy policy governs your use of the Ximera website (the
  ``Website'').
\end{abstract}
\maketitle

\section{What information does the Website obtain and how is it used?}

\subsection{User Provided Information}

The Website obtains the information you provide when you interact with
the Website. Registration with us is optional. However, please keep in
mind that you may not be able to use some of the features offered by
the Website unless you register with us.

When you register with us and use the Website, you generally
provide~(a) your name, email address, password, and other registration
information; (b) answers and interaction information, such as when you
respond to questions, engage with the interactive textbook elements,
or use the JavaScript code provided by us; (c) information you provide
us when you contact us for help; and (d) information you enter into
our system when using the Website.

We may also use the information you provided us to contact your from
time to time to provide you with important information, such as
required notices.

\subsection{Automatically Collected Information}~

In addition, the Website may collect certain information
automatically, including, but not limited to, the type of browser you
use, your browser's unique identifying information, the IP address of
your network connection, your operating system, the type of Internet
browsers you use, and information about the way you use the Website.

\subsection{Does the Website collect precise real time location
  information of the
  device?}

This Website does not collect precise information about the location
of your computer.

\subsection{Do third parties see and/or have access to information
  obtained by the Website?}

Only aggregated, anonymized data is periodically transmitted to
external services to help us improve the Website and our service. We
will share your information with third parties only in the ways that
are described in this privacy statement.

We may disclose User Provided and Automatically Collected Information:
\begin{itemize}
\item
  as required by law, such as to comply with a subpoena, or similar
  legal process;
\item
  when we believe in good faith that disclosure is necessary to protect
  our rights, protect your safety or the safety of others, investigate
  fraud, or respond to a government request;
\item
  with our trusted services providers who work on our behalf, do not
  have an~independent use of the information we disclose to them, and
  have agreed to adhere~to the rules set forth in this privacy
  statement.
\end{itemize}

You will be notified via email and/or a prominent notice on our Web
site of any change in ownership or uses of this information, as well
as any choices you may have regarding this information.

\section{What are my opt-out rights?}

You can stop all collection of information by the Website easily by no
longer visiting the Website.  You can also request to opt-out via
email, at ximera@math.osu.edu.

\section{Data Retention Policy, Managing Your Information}

We will retain User Provided data for as long as you use the Website
and for a reasonable time thereafter. We will retain Automatically
Collected information indefinitely. If you'd like us to delete User
Provided Data that you have provided via the Website, please contact
us at ximera@math.osu.edu and we will respond in a reasonable time.

\section{Children}\label{children}

We do not use the Website to knowingly solicit data from or market to
children under the age of 13. If a parent or guardian becomes aware
that his or her child has provided us with information without their
consent, he or she should contact us at ximera@math.osu.edu. We will
delete such information from our files within a reasonable time.

\section{Security}

We are concerned about safeguarding the confidentiality of your
information. We provide physical, electronic, and procedural
safeguards to protect information we process and maintain. For
example, we limit access to this information to authorized employees
and contractors who need to know that information in order to operate,
develop or improve our Website. Please be aware that, although we
endeavor provide reasonable security for information we process and
maintain, no security system can prevent all potential security
breaches.

\section{Changes}

This Privacy Policy may be updated from time to time for any reason. We
will notify you of any changes to our Privacy Policy by posting the new
Privacy Policy~here~and~informing you via email or text message. You are
advised to consult this Privacy Policy regularly for any changes, as
continued use is deemed approval of all changes. You can check the
history of this policy by clicking here.


\section{Your Consent}

By using the Website, you are consenting to our processing of your
information as set forth in this Privacy Policy now and as amended by
us. ``Processing,'' means using cookies on a computer/hand held device
or using or touching information in any way, including, but not
limited to, collecting, storing, deleting, using, combining and
disclosing information, all of which activities will take place in the
United States. If you reside outside the United States~your
information will be transferred, processed and stored there under
United States~privacy standards.~

\section{Contact us}

If you have any questions regarding privacy while using the Website,
or have questions about our practices, please contact us via email
at ximera@math.osu.edu.

\end{document}
